\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
Balance columns on last page
updated section 5.2

The fact that participants have lower average fixation duration on the
reference side in the interaction phase in the {\sf TRUE} condition than the
other two conditions actually supports the explanation that participants
with {\sf TRUE} condition had a higher initial belief in their cognitive model
of how does the robot work (Figure 6). They did not need to look onto
the reference given in observation phase. This also verifies our working
hypothesis that a carefully designed mapping between the robot's
behaviour and its visual actuators can help in maximising the learning
effect during the interaction.

@@

We indeed were interested in accessing and understanding the cognitive
mechanisms at stake during the interaction: where do participants look when they
want to understand a robot behaviour? Does \emph{anticipation} for instance
reflect understanding? How the robot's design impact the interaction? These kind
of questions are common in HRI, and ee believe that mobile eye-tracking, as a
relatively non-invasive yet accurate (both spatially and temporally) biometric
measurement, is a valuable tool to investigate them in ecologically
valid environments.

>>>>

The fact that participants have lower average fixation duration on the
reference side in the interaction phase in the {\sf TRUE} condition than the
other two conditions actually supports the explanation that participants
with {\sf TRUE} condition had a higher initial belief in their cognitive model
of how does the robot work (Figure 6). They did not need to look onto
the reference given in observation phase. This also verifies our working
hypothesis that a carefully designed mapping between the robot's
behaviour and its visual actuators can help in maximising the learning
effect during the interaction. It is important to highlight the fact that the previous two interpretations combine the behaviour of the participants, the experimental condition and the gaze measures. Thus eye-tracking provide a strong tool to form and verify cognitive hypotheses to interpret the social behaviour in human-robot interaction.

We can also have a similar interpretation from the relation between the fixation counts and the first improvement. The fact that there is a negative correlation  between the number of
fixations on the reference side (Figure~\ref{res4}) during the interaction phase
and the first Improvement also reflects that those participants who had higher belief in their initial mental models did not look at the reference side in the interaction phase and failed in the first trial. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We indeed were interested in accessing and understanding the cognitive
mechanisms at stake during the interaction: where do participants look when they
want to understand a robot behaviour? Does \emph{anticipation} for instance
reflect understanding? How the robot's design impact the interaction? These kind
of questions are common in HRI, and we believe that mobile eye-tracking, as a
relatively non-invasive yet accurate (both spatially and temporally) biometric
measurement, is a valuable tool to investigate them in ecologically
valid environments.
